\documentclass[ ../main.tex]{subfiles}
\providecommand{\mainx}{..}
\begin{document}
\section{Implementation of oblivious sets}
Kerckhoffs's principle. Shannon's maxim.

The \gls{gls-phf} described in \cref{sec:phf} is an \gls{gls-approxset} over the universe of bit strings $\BitSet^{*}$. However, injections from a countable set $\Set{X}$ to the set $\BitSet^{*}$ exist. Let us denote such an injection by
\begin{equation}
    \Encode \colon \Set{X} \mapsto \BitSet^{*}\,,
\end{equation}
which maps every element $x \in \Set{X}$ to a unique element $y \in \BitSet^{*}$. Note that in the \gls{gls-phf}, iterating over (or retrieving) elements is not supported and thus \Encode does not need to be decodable.

For instance, if elements of type $\Set{X}$ are a data structure, then \Encode may be its serialization, a \emph{linear} sequence of bits.\footnote{The \emph{memory-resident} representation is machine and process-dependent and thus not a suitable representation if the \emph{typed} \gls{gls-phf} is suppose to work across multiple machines or processes.} Alternatively, if the data structure is intended to be efficiently inserted into a \gls{gls-phf}, then something like a simple \emph{hash code} may be used since it does not need to be \emph{decodable}.\footnote{If each element of $\Set{X}$ does not uniquely map to a hash code, then the \gls{gls-fprate} as given by $\fprate$ is only an approximation.}

Consequently, we may map any set $\Set{S}_{\Set{X}} \subset \Set{X}$ to a set $\Set{S}_{\BitSet^{*}} \subset \BitSet^{*}$ so that the \gls{gls-phf} may approximate it.
We denote this the \gls{gls-phf} of type $\Set{X}$.
The \gls{gls-phf} of type $\Set{X}$ may approximate any \emph{finite set} $\Set{S}_{\Set{X}}$ where the elements are members of the countable set $\Set{X}$.
See \cref{alg:PHF} for an algorithmic description of $\MakeApproxSet$ and \cref{alg:PHF_has} for an algorithmic description of the membership predicate.
\begin{algorithm}[h]
    \caption{Implementation of \protect\MakeApproxSet for the \emph{typed} Perfect Hash Filter}
    \label{alg:typedPHF}
    \SetKwProg{func}{function}{}{}
    \KwIn
    {
        \begin{itemize}
            \item[$\Set{S}_{\Set{X}}$] The set to approximate where the universe of elements is $\Set{X}$.
            \item[$\fprate$] The false positive rate.
            \item[$r$] The load factor.
        \end{itemize}
    }
    \KwOut
    {
        A \emph{typed} \gls{gls-phf} $\Sp_{\Set{X}}$ that approximates $\Set{S}_{\Set{X}}$ with a false positive rate $\fprate$ and a load factor $r$.
    }
    \func{\MakeTypeApproxSet{$\Set{S}_{\Set{X}}$, $\fprate$ $\given$ $r$}}
    {
        $\Set{S}_\BitSet^{*} \gets \left\{ \Encode(x) \colon x \in \Set{S}_{\Set{X}}\right\}$\;
        $\Sp_{\BitSet^{*}} \gets$ \MakeApproxSet{$\Set{S}_\BitSet^{*}$, $\fprate$ $\given$ $r$}\;
        \Return $\Sp_{\Set{X}}$\;
    }
\end{algorithm}
\begin{algorithm}[h]
    \caption{Implementation of \protect\Contains for the \emph{typed} Perfect Hash Filter}
    \label{alg:typed_PHF_contains}
    \SetKwProg{func}{function}{}{}
    \KwIn
    {
        \begin{itemize}
            \item[$\PASet{S}_{\Set{X}}$] The \emph{typed} \gls{gls-phf} that approximates $\Set{S}_{\Set{X}} \subset \Set{X}$ with a false positive rate $\fprate$ and a load factor $r$.
            \item[$u$] The element in $\Set{X}$ to test membership in $\PASet{S}_{\Set{X}}$.
        \end{itemize}
    }
    \KwOut
    {
        Returns $\True$ if $x \in \Set{S}_{\Set{X}}$. Otherwise, returns \True with probability $\fprate$ and \False with probability $1 - \fprate$.
    }
    \func{\Contains{$\PASet{S}_{\Set{X}}$, $x$}}
    {
        $b \gets \Encode_\Set{X}(x)$\;
        $q \gets$ \Contains{$\PASet{S}_\BitSet^{*}$, $b$}\;
        \Return $q$\;
    }
\end{algorithm}

\subsection{C++ implementation}
Stuff for C++ goes here.
\end{document}